Large Scale Marine Protected Areas

### 2019-01-23 docs/PIPA_Palau.tex
Updated manuscript, ready to print and proof read before sending to John

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
for each model. Top panel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate. [QUESTION FOR JC: delete the intercept panel.]}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
spatial distribution of fishing effort by treated and control vessels.
Colors have been adjusted relative to the maximum observed by group and
year. Red polygons show LGMPAs in the region. For visualization purposes
only some years are presented, the full 2012 - 2017 period is shown in
Figure \ref{fig:fishing_raster_full}. [QUESTION FOR JC: we should include all years in the main text. Is there a way to normalize this, e,g. color corresponds to \% of total fishing effort, so it's easier to compare?]}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA by region. Colors indicate the pre- and post- periods. Solid line
across points shows local mean with a region-specific loess smoother.
Vertical dashed lines indicates dates when satellites were added, solid vertical
line indicates PIPA closure. Note that inflection points of
the loess smoother are not affected by the addition of satellites. [QUESTION FOR JC: this figure needs a lot of work. subplot titles need to be more intuitive. I would combine all EEZ KIR into one group and all HS KIR into one group.]}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}Coefficient
estimates for the redistribution regression. Each panel shows the
region-specific coefficients, with heteroskedasticity-robust standard
errors as error bars. The horizontal dashed line represents 0 change
relative to the 2012 region-specific levels. [QUESTION FOR JC: just do 95\% confidence intervals.]}
\end{figure}

\begin{table}

\caption{\label{tab:unnamed-chunk-16}\label{tab:mean_change}Coefficient estimates for the interaction of year and region. Each row represents a region, each column a year. Numbers in parentheses are heteroskedaticity-robust standard errors. R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001). * < 0.1; ** p < 0.05; ***p < 0.01.}
\centering
\begin{tabular}[t]{llllll}
\toprule
term & 2013 & 2014 & 2015 & 2016 & 2017\\
\midrule
PIPA PIPA 1 & -0.062 (0.026)** & 0.085 (0.043)** & -0.086 (0.026)*** & -0.079 (0.025)*** & -0.074 (0.025)***\\
EEZ KIR 1 & -0.034 (0.030) & 0.035 (0.038) & 0.042 (0.045) & -0.035 (0.031) & -0.023 (0.032)\\
EEZ KIR 2 & 0.001 (0.009) & 0.032 (0.019)* & 0.142 (0.061)** & 0.014 (0.013) & 0.014 (0.015)\\
EEZ KIR 3 & -0.188 (0.075)** & -0.061 (0.072) & -0.118 (0.069)* & -0.093 (0.083) & -0.098 (0.083)\\
HS KIR 1 & -0.003 (0.011) & 0.016 (0.012) & 0.038 (0.013)*** & 0.004 (0.013) & 0.037 (0.018)**\\
\addlinespace
HS KIR 2 & 0.009 (0.006) & 0.004 (0.006) & -0.000 (0.009) & 0.022 (0.010)** & 0.008 (0.006)\\
HS KIR 3 & -0.002 (0.009) & 0.003 (0.009) & -0.008 (0.011) & 0.022 (0.011)* & 0.064 (0.024)***\\
HS HS 1 & 0.021 (0.015) & 0.027 (0.017) & 0.045 (0.017)*** & 0.030 (0.017)* & 0.014 (0.015)\\
EEZ FSM 1 & 0.018 (0.033) & -0.015 (0.025) & 0.000 (0.037) & 0.012 (0.025) & -0.001 (0.021)\\
EEZ MHL 1 & 0.037 (0.022) & 0.025 (0.010)** & -0.006 (0.009) & 0.052 (0.032) & -0.000 (0.006)\\
\addlinespace
EEZ NRU 1 & 0.046 (0.021)** & 0.044 (0.020)** & 0.003 (0.017) & 0.033 (0.015)** & 0.050 (0.025)**\\
EEZ PNG 2 & 0.196 (0.072)*** & -0.106 (0.041)*** & -0.132 (0.043)*** & -0.064 (0.048) & 0.001 (0.049)\\
EEZ SLB 1 & 0.083 (0.056) & -0.019 (0.032) & -0.009 (0.038) & 0.081 (0.053) & 0.076 (0.046)*\\
EEZ TUV 1 & -0.055 (0.037) & -0.033 (0.040) & -0.063 (0.037)* & 0.018 (0.046) & -0.026 (0.038)\\
HS COK 1 & -0.003 (0.008) & -0.004 (0.008) & -0.003 (0.011) & -0.007 (0.008) & -0.003 (0.008)\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:sp_corr}Number of cells that
had treated and control vessels (A) and spatial correlation in the
presence-absence of treated and control vessels per cell (B).}
\end{figure}

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}

\hypertarget{stream-of-data-by-vessel-group-and-period}{%
\subsection{Stream of data by vessel, group, and
period}\label{stream-of-data-by-vessel-group-and-period}}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
		number of vessels by month for all vessels. Vertical dashed lines
		indicates dates when satellites were added, solid line indicates PIPA
		closurePIPA closure.}
\end{figure}

\hypertarget{longliners}{%
\subsection{Longliners}\label{longliners}}

Longliners show a similar pattern of effort reduction. However, the
magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
including month and flag FEs for the general treatment-control groups,
or when excluding Chinese vessels. This, along with higher standard
error values suggest that longliners have a smaller and more variable
response to the implementation of LSMPAs.

\begin{table}[!htbp] \centering 
  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications. The first three columns use all data for controls. Columns 4 - 6 exclude Chinese vessels. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
  & & & & & & \\ 
 post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
  & & & & & & \\ 
 treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
  & & & & & & \\ 
 sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
  & & & & & & \\ 
 sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
  & & & & & & \\ 
 post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Control & All & All & All & -CHN & -CHN & -CHN \\ 
Month FE & No & Yes & Yes & No & Yes & Yes \\ 
Flag FE & No & No & Yes & No & No & Yes \\ 
Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\hypertarget{quarterly-did-interactions}{%
\subsubsection{Quarterly DID
interactions}\label{quarterly-did-interactions}}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

\hypertarget{year-month-did-interactions}{%
\subsubsection{Year-month DID
interactions}\label{year-month-did-interactions}}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

\hypertarget{other-measures-of-change-in-behavior}{%
\subsection{Other measures of change in
behavior}\label{other-measures-of-change-in-behavior}}

Global Fishing Watch data includes two variables of interest that are
readily available: distance from shore and distance from port. We use
these as variables of interest and perform the following regression:

\[
y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
\]

Where \(y\) is our variable of interest, \(Year\) represent year
dummies, with 2012 as the reference level, and \(Treated\) indicates
wether a vessel belongs to the treated or control group.

\hypertarget{distance-from-shore}{%
\subsubsection{Distance from shore}\label{distance-from-shore}}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & distance\_from\_shore \\ 
\hline \\[-1.8ex] 
 Constant & 233,057.900$^{***}$ \\ 
  & (1,558.294) \\ 
  & \\ 
 year\_c2013 & $-$818.044 \\ 
  & (2,623.263) \\ 
  & \\ 
 year\_c2014 & 14,220.260$^{***}$ \\ 
  & (1,701.637) \\ 
  & \\ 
 year\_c2015 & 140,980.200$^{***}$ \\ 
  & (1,668.140) \\ 
  & \\ 
 year\_c2016 & 32,557.750$^{***}$ \\ 
  & (1,584.182) \\ 
  & \\ 
 year\_c2017 & 168,283.100$^{***}$ \\ 
  & (1,653.912) \\ 
  & \\ 
 treated & $-$11,371.280$^{***}$ \\ 
  & (1,688.879) \\ 
  & \\ 
 year\_c2013:treated & 62,899.900$^{***}$ \\ 
  & (3,274.205) \\ 
  & \\ 
 year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
  & (1,834.090) \\ 
  & \\ 
 year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
  & (1,821.587) \\ 
  & \\ 
 year\_c2016:treated & 72,512.980$^{***}$ \\ 
  & (1,739.976) \\ 
  & \\ 
 year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
  & (1,805.322) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 4,937,666 \\ 
R$^{2}$ & 0.032 \\ 
Adjusted R$^{2}$ & 0.032 \\ 
Residual Std. Error & 297,128.600 (df = 4937654) \\ 
F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\hypertarget{distance-from-ports}{%
\subsubsection{Distance from ports}\label{distance-from-ports}}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:dist_port}Regression results for distance from shore} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & distance\_from\_port \\ 
\hline \\[-1.8ex] 
 Constant & 362.707$^{***}$ \\ 
  & (1.971) \\ 
  & \\ 
 year\_c2013 & 9.082$^{***}$ \\ 
  & (3.198) \\ 
  & \\ 
 year\_c2014 & 105.414$^{***}$ \\ 
  & (2.148) \\ 
  & \\ 
 year\_c2015 & 357.746$^{***}$ \\ 
  & (2.113) \\ 
  & \\ 
 year\_c2016 & 112.441$^{***}$ \\ 
  & (2.009) \\ 
  & \\ 
 year\_c2017 & 356.506$^{***}$ \\ 
  & (2.099) \\ 
  & \\ 
 treated & 149.653$^{***}$ \\ 
  & (2.249) \\ 
  & \\ 
 year\_c2013:treated & 26.366$^{***}$ \\ 
  & (4.125) \\ 
  & \\ 
 year\_c2014:treated & 50.808$^{***}$ \\ 
  & (2.453) \\ 
  & \\ 
 year\_c2015:treated & $-$151.268$^{***}$ \\ 
  & (2.422) \\ 
  & \\ 
 year\_c2016:treated & $-$49.445$^{***}$ \\ 
  & (2.311) \\ 
  & \\ 
 year\_c2017:treated & $-$252.334$^{***}$ \\ 
  & (2.390) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 4,937,666 \\ 
R$^{2}$ & 0.047 \\ 
Adjusted R$^{2}$ & 0.047 \\ 
Residual Std. Error & 391.757 (df = 4937654) \\ 
F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\hypertarget{effort-redistribution}{%
\subsection{Effort redistribution}\label{effort-redistribution}}

\hypertarget{rasterized-regions}{%
\subsubsection{Rasterized regions}\label{rasterized-regions}}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
regions. Each color (number) indicates a distinct region.}
\end{figure}

\hypertarget{fishing-raster}{%
\subsubsection{Fishing raster}\label{fishing-raster}}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
\caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly
rasters of fishing hours for each group.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{img/other_specifications.pdf}
\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
for our variables of interest using different model specifications. Table \ref{tab:main_DID}
reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/fishing_raster.png}
\caption{\label{fig:fishing_raster}Yearly
spatial distribution of fishing effort by treated and control vessels.
Color corresponds to \% of total fishing effort in each panel.
Red polygons show LSMPAs in the region.}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/redist_trend.pdf}
\caption{\label{fig:redist_trend}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA by region. Colors indicate the pre- and post- periods. Solid line
across points shows local mean with a region-specific loess smoother.
Vertical dashed lines indicates dates when satellites were added, solid vertical
line indicates PIPA closure. Note that inflection points of
the loess smoother are not affected by the addition of satellites.}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/mean_change.pdf}
\caption{\label{fig:mean_change}Coefficient
estimates for the redistribution regression. Each panel shows the
region-specific coefficients, with 95\% condifence intervals
as error bars. The horizontal dashed line represents 0 change
relative to the 2012 region-specific levels.}
\end{figure}

\input{tab/mean_change}

\begin{figure}
\centering
\includegraphics{img/sp_corr.pdf}
\caption{\label{fig:sp_corr}Number of cells that
had treated and control vessels (A) and spatial correlation in the
presence-absence of treated and control vessels per cell (B).}
\end{figure}

\input{tab/sp_corr}

@@

%\clearpage
%
%\hypertarget{appendix}{%
%\section{Appendix}\label{appendix}}
%
%\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
%
%\hypertarget{stream-of-data-by-vessel-group-and-period}{%
%\subsection{Stream of data by vessel, group, and
%period}\label{stream-of-data-by-vessel-group-and-period}}

%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
%\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
%fishing events by vessels through time. Each line represents a vessel,
%with dots indicating months with fishing activity and colors indicating
%the pre and post periods.}
%\end{figure}

%\clearpage

%\begin{figure}
%	\centering
%	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
%	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
%		number of vessels by month for all vessels. Vertical dashed lines
%		indicates dates when satellites were added, solid line indicates PIPA
%		closurePIPA closure.}
%\end{figure}

%\clearpage

%\hypertarget{longliners}{%
%\subsection{Longliners}\label{longliners}}

%Longliners show a similar pattern of effort reduction. However, the
%magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
%including month and flag FEs for the general treatment-control groups,
%or when excluding Chinese vessels. This, along with higher standard
%error values suggest that longliners have a smaller and more variable
%response to the implementation of LSMPAs.

%\begin{table}[!htbp] \centering 
%  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications. The first three columns use all data for controls. Columns 4 - 6 exclude Chinese vessels. Numbers in parentheses are heteroskedastic-robust standard errors.} 
%  \label{} 
%\small 
%\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
%\\[-1.8ex]\hline 
%\hline \\[-1.8ex] 
% & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
%\cline{2-7} 
%\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
%\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
%\hline \\[-1.8ex] 
% Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
%  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
%  & & & & & & \\ 
% post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
%  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
%  & & & & & & \\ 
% treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
%  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
%  & & & & & & \\ 
% sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
%  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
%  & & & & & & \\ 
% sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
%  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
%  & & & & & & \\ 
% post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
%  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
%  & & & & & & \\ 
%\hline \\[-1.8ex] 
%Control & All & All & All & -CHN & -CHN & -CHN \\ 
%Month FE & No & Yes & Yes & No & Yes & Yes \\ 
%Flag FE & No & No & Yes & No & No & Yes \\ 
%Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
%R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
%\hline 
%\hline \\[-1.8ex] 
%\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
%\end{tabular} 
%\end{table}
%
%\clearpage
%
%\hypertarget{quarterly-did-interactions}{%
%\subsubsection{Quarterly DID
%interactions}\label{quarterly-did-interactions}}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
%\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
%and treatment. Control group is all vessels.}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
%\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
%and treatment. Control group is vessels from PNA.}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
%\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
%and treatment. Control group excludes Chinese vessels.}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
%\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
%and treatment. Control group is japanese vessels.}
%\end{figure}
%
%\hypertarget{year-month-did-interactions}{%
%\subsubsection{Year-month DID
%interactions}\label{year-month-did-interactions}}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
%\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
%year-month and treatment. Control group is all vessels.}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
%\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
%year-month and treatment. Control group is vessels from PNA.}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
%\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
%year-month and treatment. Control group excludes Chinese vessels.}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
%\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
%year-month and treatment. Control group is japanese vessels.}
%\end{figure}
%
%\hypertarget{other-measures-of-change-in-behavior}{%
%\subsection{Other measures of change in
%behavior}\label{other-measures-of-change-in-behavior}}
%
%Global Fishing Watch data includes two variables of interest that are
%readily available: distance from shore and distance from port. We use
%these as variables of interest and perform the following regression:
%
%\[
%y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
%\]
%
%Where \(y\) is our variable of interest, \(Year\) represent year
%dummies, with 2012 as the reference level, and \(Treated\) indicates
%wether a vessel belongs to the treated or control group.
%
%\clearpage
%
%\hypertarget{distance-from-shore}{%
%\subsubsection{Distance from shore}\label{distance-from-shore}}
%
%\begin{table}[!htbp] \centering 
%  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
%  \label{} 
%\begin{tabular}{@{\extracolsep{5pt}}lc} 
%\\[-1.8ex]\hline 
%\hline \\[-1.8ex] 
% & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
%\cline{2-2} 
%\\[-1.8ex] & distance\_from\_shore \\ 
%\hline \\[-1.8ex] 
% Constant & 233,057.900$^{***}$ \\ 
%  & (1,558.294) \\ 
%  & \\ 
% year\_c2013 & $-$818.044 \\ 
%  & (2,623.263) \\ 
%  & \\ 
% year\_c2014 & 14,220.260$^{***}$ \\ 
%  & (1,701.637) \\ 
%  & \\ 
% year\_c2015 & 140,980.200$^{***}$ \\ 
%  & (1,668.140) \\ 
%  & \\ 
% year\_c2016 & 32,557.750$^{***}$ \\ 
%  & (1,584.182) \\ 
%  & \\ 
% year\_c2017 & 168,283.100$^{***}$ \\ 
%  & (1,653.912) \\ 
%  & \\ 
% treated & $-$11,371.280$^{***}$ \\ 
%  & (1,688.879) \\ 
%  & \\ 
% year\_c2013:treated & 62,899.900$^{***}$ \\ 
%  & (3,274.205) \\ 
%  & \\ 
% year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
%  & (1,834.090) \\ 
%  & \\ 
% year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
%  & (1,821.587) \\ 
%  & \\ 
% year\_c2016:treated & 72,512.980$^{***}$ \\ 
%  & (1,739.976) \\ 
%  & \\ 
% year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
%  & (1,805.322) \\ 
%  & \\ 
%\hline \\[-1.8ex] 
%Observations & 4,937,666 \\ 
%R$^{2}$ & 0.032 \\ 
%Adjusted R$^{2}$ & 0.032 \\ 
%Residual Std. Error & 297,128.600 (df = 4937654) \\ 
%F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
%\hline 
%\hline \\[-1.8ex] 
%\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
%\end{tabular} 
%\end{table}
%
%\clearpage
%
%\hypertarget{distance-from-ports}{%
%\subsubsection{Distance from ports}\label{distance-from-ports}}
%
%\begin{table}[!htbp] \centering 
%  \caption{\label{tab:dist_port}Regression results for distance from shore} 
%  \label{} 
%\begin{tabular}{@{\extracolsep{5pt}}lc} 
%\\[-1.8ex]\hline 
%\hline \\[-1.8ex] 
% & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
%\cline{2-2} 
%\\[-1.8ex] & distance\_from\_port \\ 
%\hline \\[-1.8ex] 
% Constant & 362.707$^{***}$ \\ 
%  & (1.971) \\ 
%  & \\ 
% year\_c2013 & 9.082$^{***}$ \\ 
%  & (3.198) \\ 
%  & \\ 
% year\_c2014 & 105.414$^{***}$ \\ 
%  & (2.148) \\ 
%  & \\ 
% year\_c2015 & 357.746$^{***}$ \\ 
%  & (2.113) \\ 
%  & \\ 
% year\_c2016 & 112.441$^{***}$ \\ 
%  & (2.009) \\ 
%  & \\ 
% year\_c2017 & 356.506$^{***}$ \\ 
%  & (2.099) \\ 
%  & \\ 
% treated & 149.653$^{***}$ \\ 
%  & (2.249) \\ 
%  & \\ 
% year\_c2013:treated & 26.366$^{***}$ \\ 
%  & (4.125) \\ 
%  & \\ 
% year\_c2014:treated & 50.808$^{***}$ \\ 
%  & (2.453) \\ 
%  & \\ 
% year\_c2015:treated & $-$151.268$^{***}$ \\ 
%  & (2.422) \\ 
%  & \\ 
% year\_c2016:treated & $-$49.445$^{***}$ \\ 
%  & (2.311) \\ 
%  & \\ 
% year\_c2017:treated & $-$252.334$^{***}$ \\ 
%  & (2.390) \\ 
%  & \\ 
%\hline \\[-1.8ex] 
%Observations & 4,937,666 \\ 
%R$^{2}$ & 0.047 \\ 
%Adjusted R$^{2}$ & 0.047 \\ 
%Residual Std. Error & 391.757 (df = 4937654) \\ 
%F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
%\hline 
%\hline \\[-1.8ex] 
%\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
%\end{tabular} 
%\end{table}
%
%\hypertarget{effort-redistribution}{%
%\subsection{Effort redistribution}\label{effort-redistribution}}
%
%\hypertarget{rasterized-regions}{%
%\subsubsection{Rasterized regions}\label{rasterized-regions}}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
%\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
%regions. Each color (number) indicates a distinct region.}
%\end{figure}
%
%\hypertarget{fishing-raster}{%
%\subsubsection{Fishing raster}\label{fishing-raster}}
%
%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
%\caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly
